Study protocol

### 2022-02-22 Manuscript/S1.Protocol.tex
added README and fixed S1 for the github page

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Study protocol}
\author{}
\date{\vspace{-2.5em}2022-02-19}

@@

Add installation and setup info here.

\hypertarget{acquisition-of-the-citaion-data}{%
\subsection{Acquisition of the citaion
data}\label{acquisition-of-the-citaion-data}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"R/Setup.R"}\NormalTok{) }\CommentTok{\# Load the framework}

\CommentTok{\# Initial query to be built on domain knowledge. It accepts OR, AND, NOT boolean}
\CommentTok{\# operators and round brackets to group terms.}
\NormalTok{query }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}((model OR models OR modeling OR network OR networks) AND}
\StringTok{(dissemination OR transmission OR spread OR diffusion) AND (nosocomial OR}
\StringTok{hospital OR "long{-}term{-}care" OR "long term care" OR "longterm care" OR}
\StringTok{"long{-}term care" OR "healthcare associated") AND (infection OR resistance OR}
\StringTok{resistant))\textquotesingle{}}

@@

\[
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)
\]

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Study protocol}
\author{}
\date{\vspace{-2.5em}2022-02-22}

@@

To use the framework clone it from
\url{https://github.com/AD-Papers-Material/BART_SystReviewClassifier}
and run the R project in the repository.

The first step is loading the code base using:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"R/Setup.R"}\NormalTok{) }\CommentTok{\# Load the framework}
\end{Highlighting}
\end{Shaded}

\hypertarget{acquisition-of-the-citation-data}{%
\subsection{Acquisition of the citation
data}\label{acquisition-of-the-citation-data}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Initial query to be built on domain knowledge. It accepts OR, AND, NOT boolean}
\CommentTok{\# operators and round brackets to group terms.}
\NormalTok{query }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}((model OR models OR modeling OR network OR networks) AND}
\StringTok{(dissemination OR transmission OR spread OR diffusion) AND (nosocomial OR}
\StringTok{hospital OR "long{-}term{-}care" OR "long term care" OR "longterm care" OR}
\StringTok{"long{-}term care" OR "healthcare associated") AND (infection OR resistance OR}
\StringTok{resistant))\textquotesingle{}}

@@

\[
Sensitivity \times Efficiency =
\frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)
\]
